Deep Neural Networks for Bilingual Lexicon Extraction

### 2014-06-08 paper/main.tex
Add maybe-useful extra future work

>>>>

Lastly, future work might acknowledge the questionable assumption that there
exists a \emph{function} between source- and target-language words: that is,
that there is one target-language output for each source-language input. This
might be overcome by explicitly working to map between VSM clusters (perhaps
filtered by part of speech) rather than precise words. % TODO worth including?
